---
title: "penguin_assignment"
output: html_document
---

```{r echo=FALSE}}

setwd("C:/Users/Caroline/OneDrive/Biology Year Three/RStudio/PenguinProject")

penguins_raw <- read.csv("C:\\Users\\Caroline\\OneDrive\\Biology Year Three\\RStudio\\PenguinProject\\data_raw\\penguins_raw.csv")
source("C:\\Users\\Caroline\\OneDrive\\Biology Year Three\\RStudio\\PenguinProject\\cleaning_function.R")

```

```{r}
cleaning <- function(data_raw){
  data_raw %>%
    remove_empty(c("rows", "cols")) %>%
    select(-starts_with("delta")) %>%
    
  clean_names()
}

penguins_clean <- cleaning(penguins_raw)
head(penguins_clean)
```

# Statistical Test

An ANOVA Test to determine whether there is any significant difference between the bill length of different species of penguin.

```{r}
# Fit a linear model to our data (using the lm function) 
# lm(response_variable ~ explanatory_variable, data)
 Model1 <- lm(culmen_length_mm ~ species, penguins_clean)
summary(Model1)
```

```{r}
# Generate an ANOVA table from that linear model (using the anova function)
anova(Model1)

```
The numerator degrees of freedom is 2
The denominator degrees of freedom is 399
The alpha value is 0.05

The given F Critical Value is 3.02236
The F Statistic is 410.6

The F Critical Value is much less than our F value, therefore our results are extremely significant and there is a significant difference between the bill lengths of different species of penguin.

```{r}
library(ggplot2)
library(ggpubr)
```

```{r}
df <- data.frame(x = c(penguins_clean$species), y = c(penguins_clean$culmen_length_mm))
df
```
```{r}
ggplot(df, aes(x, y, desc_stat = "mean_sd", error.plot = "errorbar",add = "mean")) +
  geom_point(aes(color=penguins_clean$species)) +
  scale_color_manual(values=c("purple", "steelblue", "skyblue")) +
  labs(title = "Bill Length by Penguin Species") +
ylab("Bill Length in mm") +
xlab("Species") +
  scale_x_discrete(labels=c("Adelie","Chinstrap","Gentoo")) +
  stat_summary(fun.data = "mean_cl_normal", geom = "crossbar")
  
```

